---
title: "publication"
author: "Juan David Marin"
date: "2023-06-28"
output: html_notebook
runtime: shiny
---

```{r}
knitr::opts_chunk$set(echo = T)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(comment = '')
knitr::opts_chunk$set(message=FALSE)
knitr::opts_chunk$set(eval = T)
```

```{r}
library(readxl)
library(tidyr)
library(dplyr)
library(tidyselect)
library(tibble)
library(rstatix)
library(FactoMineR)
library(factoextra)
library(DT)
library(patchwork)
library(shiny)
library(ggstatsplot)
library(plotly)
library(GGally)
library(ggpubr)
```

```{r}

data <- read.csv('brand_study.csv', sep = ';', dec = '.', header = T, stringsAsFactors = T)
data <- column_to_rownames(data, var = 'sample')
head(data)

```
```{r}
data_std <- data %>% 
  dplyr::select_if(is.numeric) %>% 
  scale()  

set.seed(123)
data_km <- kmeans(data_std, centers = 3)

data_clus <- data %>% 
  cbind(clus = as.factor(data_km$cluster))
```

## Correlation analysis 


```{r }
numeric <- data %>% 
  select_if(is.numeric) 


selectInput(inputId = 'corr',label = 'Select a numeric variable for correlation analysis.',
            choices = names(numeric), selected = names(numeric)[5], multiple = F)

renderPrint(
  # p values
  sapply(numeric, function(x) round(cor.test(x, numeric[,c(input$corr)])$p.value,5))
)
renderPrint(
  # Correlation
  sapply(numeric, function(x) round(cor.test(x, numeric[,c(input$corr)])$estimate,2))
)
```


```{r}
# round(sapply(numeric, function(x) cor.test(x, numeric[,c('var_A5')])$estimate),2)
```
Los p valor de las correlaciones entre las variables son menores a 0.05, por lo tanto son estadisticamente distintas de cero, adicional, laas correlaciones son positivas y altas. a exepcion de la variable var_A3


## Partial correlation.

```{r}

library(ppcor)
selectInput(inputId = 'cv1',label = 'Select a variable 1',
            choices = names(numeric), selected = names(numeric)[5], multiple = F)
selectInput(inputId = 'cv2',label = 'Select a variable 2',
            choices = names(numeric), selected = names(numeric)[10], multiple = F)
selectInput(inputId = 'cv3',label = 'Select a control variable',
            choices = names(numeric), selected = names(numeric)[3], multiple = F)
renderPrint(
  pcor.test(x = numeric[,input$cv1],
            y = numeric[,input$cv2],
            z = numeric[,input$cv3])
)
```

```{r}
pcor.test(x = numeric[,'var_A1'],
            y = numeric[,'var_A2'],
            z = numeric[,'var_A5'])
```




## Correlation plot

```{r}
numeric <- data_clus %>% 
  select_if(is.numeric)
selectInput(inputId = 'numerical_df',label = 'Select a numeric variable',
            choices = names(numeric), selected = names(numeric), multiple = T)


# Creando DF con lo seleccionado en los select input
df_interactive <- reactive({
    cbind(data_clus[input$numerical_df])
  })

library(corrplot)
renderPlot(
df_interactive() %>% 
  #dplyr::select(-class,-brand) %>% 
  cor() %>% 
  corrplot(method = "ellipse",type = "lower", tl.cex = 1,
           order = "hclust", insig = "pch", tl.col='black',
           addCoef.col = 'black', number.cex =0.9, number.font = 5,
           col = COL2('PiYG'))
)
```






## Lineal models 

```{r warning=FALSE}
numeric <- data %>% 
  select_if(is.numeric) 

selectInput(inputId = 'lm',label = 'Select a numeric variable for LM',
            choices = names(numeric), selected = names(numeric)[5], multiple = F)
renderPrint(
sapply(numeric, function(x) round(summary(lm(x ~ numeric[,c(input$lm)]))$r.squared,2))
)

```



## Models plots

```{r}
library(shiny)
selectInput(inputId = 'lmx',label = 'Select a numeric variable for for x axis',
            choices = names(numeric), selected = names(numeric)[5], multiple = F)
selectInput(inputId = 'lmy',label = 'Select a numeric variable for y axis',
            choices = names(numeric), selected = names(numeric)[1], multiple = F)
checkboxInput(inputId = 'tf', label = 'Show ellipse', value = F)

renderPlot(
data_clus %>% 
  ggscatter(x = input$lmx, y = input$lmy, add = 'reg.line', color = 'clus',
             palette = "jco", ellipse = input$tf, ellipse.level = 0.95,ellipse.alpha = 0.1,
            ellipse.border.remove = T,mean.point = input$tf,ellipse.type = "norm",
            add.params = list(color = "red")) +
    stat_cor(label.x.npc = "left", label.y.npc = "top", 
            aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) +
  stat_regline_equation(label.x.npc = 'center', label.y.npc = 'top')
)
```


For the predictions of the rest variables I will choose the var_B5 for those physicochemical variables type B and var_A5 for those type A as independent variables

```{r}
cor(data_clus$var_B2, data_clus$var_A4)
```


```{r}
summary(lm(data_clus$var_B2 ~ data_clus$var_A4))
```



```{r}
data_clus %>% 
  ggscatter(x = 'var_B2', y = 'var_A4', add = 'reg.line', color = 'clus',
            palette = "jco", ellipse = T, ellipse.level = 0.95,ellipse.alpha = 0.1,
            ellipse.border.remove = T,mean.point = T,ellipse.type = "norm",
            add.params = list(color = "red")) +
  stat_cor(label.x.npc = "left", label.y.npc = "top", digits = 4,
            aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) +
  stat_regline_equation(label.x.npc = 'center', label.y.npc = 'top')
```




# Linear models for Variables measured with chemical measuring equipment type A

```{r}
data[26,]
```



```{r}
#var_A5 <- data.frame(var_A5 = 6.2775)
var_A5 <- data.frame(var_A5 = 1.4)

model_A1 <- lm(var_A1 ~ var_A5, data = data)
model_A2 <- lm(var_A2 ~ var_A5, data = data)
model_A3 <- lm(var_A3 ~ var_A5, data = data)
model_A4 <- lm(var_A4 ~ var_A5, data = data)

pred_A1 <- predict(model_A1, var_A5)
pred_A2 <- predict(model_A2, var_A5)
pred_A3 <- predict(model_A3, var_A5)
pred_A4 <- predict(model_A4, var_A5)
```

# Linear models for Variables measured with chemical measuring equipment type B

```{r}
#var_B5 <- data.frame(var_B5 = 1026.41)
var_B5 <- data.frame(var_B5 = 295.3)
model_B1 <- lm(var_B1 ~ var_B5, data = data)
model_B2 <- lm(var_B2 ~ var_B5, data = data)
model_B3 <- lm(var_B3 ~ var_B5, data = data)
model_B4 <- lm(var_B4 ~ var_B5, data = data)

pred_B1 <- predict(model_B1, var_B5)
pred_B2 <- predict(model_B2, var_B5)
pred_B3 <- predict(model_B3, var_B5)
pred_B4 <- predict(model_B4, var_B5)
```




```{r}
prediction = cbind(var_A1 = pred_A1,var_A2 = pred_A2, var_A3 = pred_A3,var_A4 = pred_A4,var_A5 = var_A5,
                   var_B1 = pred_B1,var_B2 = pred_B2,var_B3 = pred_B3,var_B4 = pred_B4,var_B5 = var_B5)
prediction
row.names(prediction) <- 'pred'
```


```{r}

original_mean <- attr(data_std, "scaled:center")
original_sd <- attr(data_std, "scaled:scale")

prediction_sc <- scale(prediction, center = original_mean, scale = original_sd ) %>% 
  as.data.frame()

clus_pred <- predict(data_km, newdata =prediction_sc)
prediction <- cbind(prediction, clus = as.factor(clus_pred) )

clus_pred
```



```{r}
data_km$cluster
```


```{r}
new_data_clus_pred <- data_clus %>% 
  dplyr::select(-class, -brand) %>% 
  rbind(prediction)
```


```{r}

selectInput(inputId = 'label',label = 'Labels', multiple = T,
            choices = c("ind", "ind.sup", "quali", "var", "quanti.sup"), selected = "ind.sup")

selectInput(inputId = 'invisible',label = 'Invisible', multiple = T,
            choices = c("ind", "ind.sup", "quali", "var", "quanti.sup"), selected = "ind")

res_pca3 <- PCA(new_data_clus_pred, graph = F,
                quali.sup = 11,
               ind.sup =30
               )
renderPlot(
fviz_pca_biplot(res_pca3,pointshape = 21, pointsize = 2,
                habillage = 11, label = c(input$label),
              invisible = c(input$invisible),
             addEllipses =TRUE,
             ellipse.alpha = 0.1,
             ellipse.type = "norm",
             alpha.var ="contrib",
             #col.var = 'black',
             col.ind.sup = "red",
             )
)
```








```{r}
## data long escalada
data_long_by_clus_scale <- new_data_clus_pred %>% 
  select_if(is.numeric) %>%
  scale() %>%
  cbind(clus = new_data_clus_pred$clus) %>% data.frame() %>% 
  tibble::rownames_to_column(var = 'names') %>% 
  gather(key = 'var', value = 'values',2:11, factor_key = T) %>% 
  group_by(clus, var) %>% 
  get_summary_stats(values, type ="mean_sd")

## Prediccion
prediction_scale_long <- prediction_sc %>% 
  cbind(clus = as.factor(clus_pred)) %>% 
  tibble::rownames_to_column(var = 'names') %>% 
  gather(key = 'var', value = 'values', 2:11) %>% 
  group_by(clus, var) %>% 
  get_summary_stats(values, type ="mean")


clus_1 <- subset(data_long_by_clus_scale, data_long_by_clus_scale$clus ==1) 
clus_2 <- subset(data_long_by_clus_scale, data_long_by_clus_scale$clus ==2)
clus_3 <- subset(data_long_by_clus_scale, data_long_by_clus_scale$clus ==3)

library(plotly)

fig <- plot_ly(
    type = 'scatterpolar',
    mode = 'lines',
    fill = 'toself'
  ) 

fig <- fig %>% 
  add_trace(
  type = 'scatterpolar',
  mode = 'lines',
  r = clus_1$mean,
  theta =clus_1$var,
  mode = 'markers',
  fill = 'toself',
  name = 'Clus 1'
)
fig <- fig %>% 
  add_trace(
  type = 'scatterpolar',
  mode = 'lines',
  r = clus_2$mean,
  theta =clus_2$var,
  mode = 'markers',
  fill = 'toself',
  name = 'Clus 2'
)
fig <- fig %>% 
  add_trace(
  type = 'scatterpolar',
  mode = 'lines',
  r = clus_3$mean,
  theta =clus_3$var,
  mode = 'markers',
  fill = 'toself',
  name = 'Clus 3'
)
fig <- fig %>% 
  add_trace(
  type = 'scatterpolar',
  mode = 'lines',
  r = prediction_scale_long$mean,
  theta =prediction_scale_long$var,
  mode = 'markers',
  fill = 'toself',
  name = 'prediction'
)

fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T
      )
    )
  )

renderPlotly(
fig
)

```




```{r}
#var_A5 <- data.frame(var_A5 = 6.2775)
var_A5 <- data.frame(var_A5 = 1.4)

model_A1 <- lm(var_A1 ~ var_A5, data = data)
model_A2 <- lm(var_A2 ~ var_A5, data = data)
model_A3 <- lm(var_A3 ~ var_A5, data = data)
model_A4 <- lm(var_A4 ~ var_A5, data = data)

pred_A1 <- predict(model_A1, var_A5)
pred_A2 <- predict(model_A2, var_A5)
pred_A3 <- predict(model_A3, var_A5)
pred_A4 <- predict(model_A4, var_A5)
```

```{r}
library(performance)
model_A <- lm(var_A1 ~ var_A5, data = data)
r2(model_A)
check_model(model_A)
```








